\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{float}
\geometry{margin=1in}
\title{NKPC HSA Bayesian State-Space Estimation: Output gap, HP filter}
\author{}
\date{\today}
\begin{document}
\maketitle

\section{Data and Transformations}
Raw data are read from \texttt{data/raw/}. Processed model-ready data are written to
\texttt{data/processed/}. The HSA competition aggregator convention is
\[
N^{model}_t=\frac{100\log(N^{level}_t)-\overline{100\log(N^{level})}}{10}.
\]
Thus \(N^{model}_t\), \(\hat N_t\), and \(\bar N_t\) are centered and measured
in ten-log-point units. If a run metadata file records another
\texttt{n\_transform}, interpret the corresponding coefficients using that
metadata.

\section{Model Specifications}
The CES benchmark is
\[
\pi_t=\alpha \pi_{t-1}+(1-\alpha)E_t\pi_{t+1}+\kappa x_t+e_t.
\]
The dynamic HSA specification is
\[
\pi_t=\alpha \pi_{t-1}+(1-\alpha)E_t\pi_{t+1}+\kappa x_t-\theta\hat N_t+e_t.
\]
The steady HSA specification is
\[
\pi_t=\alpha \pi_{t-1}+(1-\alpha)E_t\pi_{t+1}+(\kappa_0+\delta\bar N_t)x_t+e_t.
\]
The both-effects HSA specification is
\[
\pi_t=\alpha \pi_{t-1}+(1-\alpha)E_t\pi_{t+1}
+(\kappa_0+\delta\bar N_t)x_t-(\theta_0+\gamma\bar N_t)\hat N_t+e_t.
\]
The maintained HSA decomposition is
\[
N_t=\hat N_t+\bar N_t,\quad
\hat N_t=\rho_1\hat N_{t-1}+\rho_2\hat N_{t-2}+u_t,\quad
\bar N_t=n+\bar N_{t-1}+\epsilon_t.
\]

\section{Unit and Covariance Conventions}
Priors for \(\kappa\), \(\kappa_0\), and \(\delta\) are specified in
physical units. Legacy Gibbs samplers internally use \texttt{KAPPA\_SCALE=100}
when the design matrix contains \(x_t/100\). All posterior draws, tables,
figures, SDDR calculations, and model-comparison summaries are reported in
physical units. The default dynamic-HSA shock covariance allows only
\((e_t,\zeta_t)\) correlation; diagonal and historical full covariance modes
are available only through explicit run metadata.
Because the default \(N\) transform is centered and divided by 10, the reported
\(\delta\), \(\theta\), \(\theta_0\), and \(\gamma\) coefficients are already
effects for a ten-log-point movement in the corresponding \(N\) component.
\(\kappa_0\) and \(\theta_0\) are intercepts at average \(\bar N_t\).

\section{Coefficient Summary}
Table~\ref{tab:pivot} reports posterior means and 95\% credible intervals for
key parameters across all four models (baseline prior, full sample).
Cells show \textit{mean} [\textit{ci\_2.5}, \textit{ci\_97.5}].

\begin{table}[H]
\centering
\caption{Posterior means and 95\% credible intervals by model}
\label{tab:pivot}
\scriptsize
\resizebox{\textwidth}{!}{\input{../tables/output_gap_hp/coefficient_means_pivot.tex}}
\end{table}

\section{Result Blocks}
Results are organized by condition. Each section fixes a data specification,
prior specification, and sample period, then reports the coefficient table,
prior/posterior overlay by model, Savage-Dickey density ratios, time-varying
\(\kappa_t\) path, and model-comparison output for that condition.
\input{../tables/output_gap_hp/result_blocks.tex}

\section{Notes}
WAIC and LOO are not used as primary criteria because the models contain
latent states. Chib marginal likelihoods are reported only when the legacy
ordinate calculation can be matched to the sampler units and supplied data.

\end{document}
